VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_eval.tex
re
chagne

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=10,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees on a $p=100$-node cluster.}
  \label{fig:pds-replication}
\end{figure}

@@

In general, our experiments show that
version detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
Similarity-guided local search can further reduce the data size
to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction to the dirty segments.
The popularity-guided global deduplication with $\sigma=2\% $
reduces the data further to 860GB, namely 8.6\% of the original size. 
So it provides additional 28.63\% reduction.

>>>>

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={Availability (\%)},
                xmin=0,
                xmax=10,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees on a $p=100$-node cluster.}
  \label{fig:pds-replication}
\end{figure}

@@

In summary, our experiments show that
version detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about a 75.86\% reduction. Namely 10TB snapshot data per machine is reduced to 2.414TB.
Similarity-guided local search can further reduce the data size
to about 1.205T, which is  12.05\% of original. Thus it delivers a 50.08\% reduction after the version-based
 deduplication.
The popularity-guided global deduplication with $\sigma=2\% $
reduces the data further to 860GB, namely 8.6\% of the original size. 
So it provides additional 28.63\% reduction.
